The imprint of global magma oceans on exoplanet demographics

### 2023-03-09 src/tex/ms.tex
fix paragraph on photometric precision/transit depth

For a transit signal to be detected in a transit survey, it must reach a sufficient signal-to-noise ratio (S/N) that is sensitive on the achieved photometric precision~\citep[e.g.,][]{Burke2015,Hardegree-Ullman2019}.
In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
To represent these photometric limits, we chose a minimum transit depth of \SI{75}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
For uncertainties in bulk density measurements, we propagate normally distributed errors of mass measurements assuming $\sigma_\mathrm{M_\mathrm{P}} = \SI{10}{\percent}$, as expected for \plato. \todo[inline]{20230307 after restructuring, check where the above sentence should go}
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

>>>>

A successful transit detection requires a sufficient signal-to-noise ratio (S/N), which is sensitive on the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for PLATO
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
In line with its requirement to detect Earth-sized planets in a \SI{1}{\year} orbit around Sun-like stars, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal~\citep[][Matuszewski et al., in prep.]{plato2017}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
For uncertainties in bulk density measurements, we propagate normally distributed errors of mass measurements assuming $\sigma_\mathrm{M_\mathrm{P}} = \SI{10}{\percent}$, as expected for \plato. \todo[inline]{20230307 after restructuring, check where the above sentence should go}
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.
